Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-02-20 docs/thesis/chap-evaluation.tex
added again literature

\section{Results quality}
In this section we are interested in evaluating the quality of the results provided by our system.
The type of queries that MASE was designed for, are typical equations that can be found in a scientific publication. 
Out main user case is that a user of CDS is interested in finding documents inside the collection whose equations are related to the one that is provided.

\subsection{Equations}
The evaluated queries were provided by physics experts working at CERN from their own research topics. The queries were provided in \LaTeX format as the users used them in their own publications.
Table \ref{equations_table} presents the set of queries that were evaluated, and a simple explanation about it.

>>>>

\section{Results quality}
In this section we are interested in evaluating the quality of the results provided by our system.
The type of queries that $5e^{x+y}$ was designed for, are typical equations that can be found in a physics scientific publication. 
Out main user case is that a user of CDS is interested in finding documents inside the collection whose equations are related to the one that is provided.

\subsection{Equations}
The evaluated queries were provided by physics experts working at CERN from their own research topics. The queries were provided in \LaTeX format as the users used them in their own publications.
Table \ref{equations_table} presents the set of queries that were evaluated, and a simple explanation about it. 
Each of the users evaluated the results only for the equations he/she provided. For each of the presented result, the user ranked it as "Completely Relevant", "Partially Relevant" and "Completely Irrelevant". As all evaluations including human interaction, this scoring is at some level subjective.

We present results for three metrics: Partial precision (Document either partially relevant or completely relevant) $P_{partial} = \frac{|Partially Relevant Results \cup Strictly Relevant Results | }{K}$, $P_{strict} = \frac{Strictly Relevant Results | }{K}$ and discounted cumulative gain.

### 2014-02-20 docs/thesis/chap-theoretical_background.tex
small additions to the document
added again literature

\section{Vector Space Model}
The vector space model\cite{vector_space_model} which was developed between the 1960s and 1970s alongside the SMART Information Retrieval System. In this model, documents (from a collection $D$) and queries are represented as vectors $d$ and $q$ in a vector space where each index term corresponds to a dimension. If a term $t_i$ occurs in a given query or document, its i-th  coordinate will have a non zero value. Index terms can be keywords or phrases in the context of textual search or any other type of feature that can be extracted from the elements in a given specific context.
The scoring of a document for a given query is computed as the cosine of the angle between both vectors which can be expressed as: 
$$score(d, q) = cos\theta = \frac{d \cdot q}{\parallel d \parallel \parallel q \parallel}  = \frac{\sum_{i=1}^{n}weight(d_i, d)*weight(q_i, q)}{\sqrt{\sum_{i=1}^{n}weight^2(d_i, d)}\sqrt{\sum_{i=1}^{n}weight^2(q_i, q)}} $$

@@

>>>>

\section{Vector Space Model}
The vector space model\cite{vector_space_model} which was developed between the 1960s and 1970s alongside the SMART Information Retrieval System. In this model, documents (from a collection $D$) and queries are represented as vectors $d$ and $q$ in a vector space where each index term corresponds to a dimension. If a term $t_i$ occurs in a given query or document, its i-th  coordinate will have a non zero value. Index terms can be keywords or phrases in the context of textual search or any other type of feature that can be extracted from the elements in a given specific context.
The scoring of a document for a given query is computed as the cosine of the angle between both vectors which can be expressed as: 
$$score(d, q) = cos\theta(d, q) = \frac{d \cdot q}{\parallel d \parallel \parallel q \parallel}  = \frac{\sum_{i=1}^{n}weight(d_i, d)*weight(q_i, q)}{\sqrt{\sum_{i=1}^{n}weight^2(d_i, d)}\sqrt{\sum_{i=1}^{n}weight^2(q_i, q)}} $$

@@

\section{Latent Semantic Indexing}
